\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-03-11 doc/src/intro.tex

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|l|}
\hline
Major identity & Minor identity & \\
\hline
\hline
0              & --             & \em Reserved by Privileged Architecture \\
\hline
1              & --             & Supervisor software interrupt \\
2              & --             & Virtual supervisor software interrupt \\
3              & --             & Machine software interrupt \\
\hline
4              & --             & \em Reserved by Privileged Architecture \\
\hline
5              & --             & Supervisor timer interrupt \\
6              & --             & Virtual supervisor timer interrupt \\
7              & --             & Machine timer interrupt \\
\hline
8              & --             & \em Reserved by Privileged Architecture \\
\hline
9              & \multicolumn{1}{l|}{Determined by}
                                & Supervisor external interrupt \\
10             & \multicolumn{1}{l|}{\ external interrupt}
                                & Virtual supervisor external interrupt \\
11             & \multicolumn{1}{l|}{\ controller}
                                & Machine external interrupt \\
\hline
12                   & -- & Supervisor guest external interrupt \\
13                   & -- & Counter overflow interrupt \\
14--15               & -- & \em Reserved by Privileged Architecture \\
\hline
\hline
16--23         & --       & \em Reserved for standard local interrupts \\
24--31         & --       & \em Designated for custom use \\
32--47         & --       & \em Reserved for standard local interrupts \\
$\geq \mbox{48}$ & --     & \em Designated for custom use \\
\hline
\end{tabular}
\end{center}
\caption{%
Major and minor identities for all interrupt causes at a hart.
Major identities 0--15 are the purview of the {\RISCV} Privileged
Architecture.%
}
\label{tab:interruptIdents}
\end{table*}

>>>>

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|l|}
\hline
Major identity & Minor identity & \\
\hline
\hline
0              & --             & \em Reserved by Privileged Architecture \\
\hline
1              & --             & Supervisor software interrupt \\
2              & --             & Virtual supervisor software interrupt \\
3              & --             & Machine software interrupt \\
\hline
4              & --             & \em Reserved by Privileged Architecture \\
\hline
5              & --             & Supervisor timer interrupt \\
6              & --             & Virtual supervisor timer interrupt \\
7              & --             & Machine timer interrupt \\
\hline
8              & --             & \em Reserved by Privileged Architecture \\
\hline
9              & \multicolumn{1}{l|}{Determined by}
                                & Supervisor external interrupt \\
10             & \multicolumn{1}{l|}{\ external interrupt}
                                & Virtual supervisor external interrupt \\
11             & \multicolumn{1}{l|}{\ controller}
                                & Machine external interrupt \\
\hline
12                   & -- & Supervisor guest external interrupt \\
13                   & -- & Counter overflow interrupt \\
14--15               & -- & \em Reserved by Privileged Architecture \\
\hline
\hline
16--23         & --       & \em Reserved for standard local interrupts \\
\hline
24--31         & --       & \em Designated for custom use \\
\hline
32--34         & --       & \em Reserved for standard local interrupts \\
35             & --       & Low-priority RAS event interrupt \\
36--42         & --       & \em Reserved for standard local interrupts \\
43             & --       & High-priority RAS event interrupt \\
44--47         & --       & \em Reserved for standard local interrupts \\
\hline
$\geq \mbox{48}$ & --     & \em Designated for custom use \\
\hline
\end{tabular}
\end{center}
\caption{%
Major and minor identities for all interrupt causes at a hart.
Major identities 0--15 are the purview of the {\RISCV} Privileged
Architecture.%
}
\label{tab:interruptIdents}
\end{table*}
